\documentclass[margin,line]{resume}
\usepackage[pdftex,
            pdfauthor={Leandro Lisboa Penz},
            pdftitle={Leandro Lisboa Penz},
            ]{hyperref}
\usepackage[utf8]{inputenc}

\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\title{Leandro Lisboa Penz}
\author{Leandro Lisboa Penz}
\begin{document}

\newcommand{\nl}[0]{\vspace{1mm}\\}

\name{\Large Leandro Lisboa Penz}
\begin{resume}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{\mysidestyle Contact information}

    Email: \hfill \href{mailto:lpenz@lpenz.org}{lpenz@lpenz.org} \\

    Homepage: \hfill \url{http://www.lpenz.org} \\
    LinkedIn: \hfill \url{https://linkedin.com/in/lpenz} \\
    Lattes CV: \hfill \url{http://lattes.cnpq.br/0824061646899870} \\
    GitHub: \hfill \url{https://github.com/lpenz} \\
    Twitter: \hfill \href{https://twitter.com/lpenz}{@lpenz} \\
    Stack Overflow: \hfill \url{https://stackoverflow.com/cv/lpenz}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{\mysidestyle About me}

    I'm currently working as an embedded software architect of DmOS ---
DATACOM's universal embedded OS. I focus on modularity, continuous
integration, incremental qualification and DevOps. I work very closely
with the DevOps team, bringing solutions and new technologies, and also
helping in general.

I was one of the architects that worked on the initial definitions of
the architecture, processes and tools used nowadays in the company. The
architecture group itself was something new back then.

Before the creation of the architecture group, I led small (8)
development teams. At first, I led teams of embedded software
development for about 5 years, as I started as a developer myself. I
then led the test infrastructure team for about a year while also acting
as a software architect for the Ethernet switch product line.

I hold a master degree in computer science from UFRGS. My research line
was on computer networks, distributed systems, fault tolerance and
security. My dissertation was about distributed firewall rule coherence.
I implemented the prototype checker in Haskell.

I hold an MBA on management and leadership from UNISINOS. I graduated in
electrical engineering from UFRGS.

I value technical excellence, out-of-the-box thinking, generalism,
strategic planning and long-term maintainability. I'm always looking for
vulnerabilities and enhancement opportunities in my knowledge and tool
set.

Out of the professional context, I have studied and obtained a license
to fly sailplanes. I can definitely say that I learned a lot from doing
that, from the differences with my area (extreme risk aversion) as well
as from the similarities (briefing/debriefing \(\sim\) sprint
planning/review).


    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{\mysidestyle Experience}

    

    

    \textbf{Arista Networks} \nl{}
    \textsl{Software engineer} \hfill \textbf{2016 - present}

    

    

    
    \clearpage
    

    \textbf{DATACOM} \nl{}
    \textsl{Embedded software architect} \hfill \textbf{2014 - 2016}

    Software architect of DATACOM's embedded universal operating system:
DmOS.
\begin{itemize}
\tightlist
\item
  Research and high-level definition the system architecture.
\item
  Design of the overall development process.
\item
  A lot of code review.
\item
  Coding of some core modules.
\end{itemize}

Software architect assigned to DevOps.
\begin{itemize}
\tightlist
\item
  Initial tooling and structuring of the DevOps infrastructure.
\item
  Definition of the DevOps process: homologation vs test vs production
  environments.
\item
  Alignment of the infrastructure with DmOS's requirements.
\item
  Coding of some of the solutions.
\end{itemize}


    

    

    \textbf{DATACOM} \nl{}
    \textsl{Leader of test automation team; embedded software architect} \hfill \textbf{2012 - 2014}

    Software Team Leader of Ethernet switch test automation team.
\begin{itemize}
\tightlist
\item
  Coordination of the team that was responsible for:
\begin{itemize}
  \tightlist
  \item
    test development: in ruby;
  \item
    test excution: 24/7, in sync with product integration;
  \item
    test infrastructure maintenance: \(\sim\) 5 testbeds, most with
    Ethernet ring topologies.
  \end{itemize}
\item
  Backlog and defect priorization.
\item
  Agile methodologies.
\item
  Performance evaluation, feedback.
\end{itemize}

Software architect of DATACOM's Ethernet switch product line:
\begin{itemize}
\tightlist
\item
  Evaluation and implementation of static analysis tools.
\item
  Development of debugging tools.
\item
  Overall development process enhancements.
\item
  I was also heavily involed with the design and implementation of tools
  that gathered data and generated development and defect metrics using
  python and django, full stack.
\end{itemize}


    

    

    \textbf{DATACOM} \nl{}
    \textsl{Leader of embedded software team} \hfill \textbf{2007 - 2011}

    Software team leader of DATACOM's NG-SDH Multiplexer product line.
\begin{itemize}
\tightlist
\item
  Coordination of distributed teams (\(\sim\) 8, about half local, half
  remote) of embedded software developers.
\item
  Guidance and reference in the development of solutions.
\item
  Backlog and defect priorization.
\item
  Agile methodologies.
\item
  Performance evaluation, feedback.
\item
  A lot of code review.
\end{itemize}


    

    

    \textbf{DATACOM} \nl{}
    \textsl{Embedded software developer} \hfill \textbf{2002 - 2007}

    Team member of the first NG-SDH Multiplexer developed in Brazil.
\begin{itemize}
\tightlist
\item
  Software development using the C linguage for embedded Linux systems:
  network servers, debug tools and drivers (kernel space).
\item
  Unix server administration and maintenance.
\item
  Script development (test automation) and scripting language extension:
  Lua, Python and TCL (Expect).
\end{itemize}


    

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{\mysidestyle Education}

    

    

    \textbf{Vale do Rio dos Sinos University (UNISINOS)} \nl{}
    \textsl{MBA - Organizational Leadership and Management} \hfill \textbf{2012 - 2013}

    Subjects:
\begin{itemize}
\tightlist
\item
  Business management
\item
  Project management
\item
  Human resources
\item
  Leadership
\item
  Organizational identity and culture
\end{itemize}


    

    
    \clearpage
    

    \textbf{Federal University of Rio Grande do Sul (UFRGS)} \nl{}
    \textsl{Master of Science, Computer Science} \hfill \textbf{2006 - 2008}

    \emph{Orientation}: Prof.~Dr.~Raul Fernando Weber\\
\emph{Research line}: fault tolerance, network security and distributed
systems.\\
\emph{Dissertation}: Coherence in distributed packet filters\\
Formal definition of the concept of anomaly in isolated and distributed
network packet filters through the use of graphs and set theory.
Development of a prototype anomaly checker in Haskell.\\
\emph{Online}: \url{http://www.lume.ufrgs.br/handle/10183/22813}


    

    

    \textbf{Federal University of Rio Grande do Sul (UFRGS)} \nl{}
    \textsl{Graduation, Electrical Engineering} \hfill \textbf{1998 - 2002}

    The program is ranked among the top in Brazil, according to the
evaluation process carried out by the CAPES agency of the Brazilian
Ministry of Education.


    

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{\mysidestyle Other courses}

    

    \textbf{Pontifícia Universidade Católica - RS} \nl{}
    \textsl{Agile methodologies: project management with SCRUM} \hfill \textbf{2009} \nl{}
    Course load: 12h

    

    

    \textbf{Vale do Rio dos Sinos University (UNISINOS)} \nl{}
    \textsl{Software project management} \hfill \textbf{2006} \nl{}
    Course load: 21h

    Study of PMI's PMBOK.


    

    \textbf{UFRGS - Data processing center} \nl{}
    \textsl{TCP/IPv4 routing - Internet high availability} \hfill \textbf{2003} \nl{}
    Course load: 16h

    Focused on network routing protocols: RIP, OSPF and BGP.


    

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{\mysidestyle Languages}

    \begin{tabular}{rl}
        
        \textsc{Portuguese:}&Native\\
        
        \textsc{English:}&Fluent\\
        
        \textsc{German:}&Basic\\
        
    \end{tabular}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{\mysidestyle Random achievements and anecdotes}

    \begin{itemize}
        
        \item I installed my first Debian GNU/Linux at home in 2003, and never
reinstalled it from scratch. I use the ``testing'' release, and update
it constantly.

        
        \item I learned Haskell while developing the prototype of my MSc dissertation
in 2006. Since then, I have used it on side projects and on programming
contests when I have the chance.

        
        \item Even though I did not take computer science at graduation, I was 6th on
the entry exam of the MSc at my University (UFRGS).

        
        \item I once got all questions right in a logical reasoning test. The
psychologist that evaluated it said that she had never seen that before.

        
        \item This CV is maintained at \url{http://github.com/lpenz/cv} with
configuration management, automated tests and continuous deployment to
\url{http://cv.lpenz.org} in several output formats.

        
    \end{itemize}
\end{resume}
\end{document}

% vim: ft=tex.jinja